%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Eric Koslow
\documentclass[margin,line]{resume}
\usepackage{hyperref}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Eric Koslow}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    135 Lyons Plain Rd                          \hfill mobile: +1(203)648-4309          \vspace{0mm}\\\vspace{0mm}%
    Weston, CT 06883                            \hfill e-mail: ekoslow@gmail.com  \vspace{0mm}\\\vspace{-4.5mm}%


    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{Rochester Institute of Technology}, Rochester, New York \vspace{2mm}\\\vspace{1mm}%
    \textsl{B.S. Software Engineering} \hfill \textbf{September 2008 -- May 2010}\vspace{-3mm}\\\vspace{-1mm}%


    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}

    \textbf{GABAE Development}, Waterloo, Ontario, Canada \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineering Co-Op} \hfill \textbf{May 2009 -- August 2009}\\
    Wrote back-end code to optimize mass insertion of data into a PostgreSQL database.
    Created simple test front-end websites using Google Web Toolkit to better visualize 
    incoming data.


    \textbf{GABAE Holding}, Addison, Texas \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineer / Investment Analyst} \hfill \textbf{May 2010 -- present}\\
    Currently fill in my services where needed.  If a programming project comes up, I program.  
    When an investment opportunity arises, I held research and do due diligence. As of April 2011, I have
    written the business plan for a green energy power plant, brought a failed informatics company 
    back from bankruptcy, designed and built a custom web-based SCADA system, and proposed a
    high risk, high yield investment strategy to add to our portfolio.


    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Programming} 

    Ruby, Rails, PHP, Java, C, HTML5/CSS3, \LaTeX, Javascript, Node. I am also comfortable learning any new language.\\
    My GitHub account is located at \url{https://github.com/ekosz} and can be used to see what new hacks
    I'm currently working on.


    %______________________________________________________________________________________________________________________
    \section{\mysidestyle Personal\\Projects} 

    \textsl{Tutorii} \hfill \textbf{Oct 2009 - May 2009}\\
    Created website Tutorii.com. Site provided a place for students to peer teach one another, 
    as well as get help with their homework and classes. The site was featured in local magazines 
    as well as local television stations. The site is no longer up, but can still be read about
    at RIT's news site ( \url{http://www.rit.edu/news/story.php?id=47197} ).


    \textsl{Mojang Valuation} \hfill \textbf{Oct 2010 - Present}\\
    Built a website to display and explain the current valuation of the company Mojang.  The site
    polls the sales data from Mojang, then uses valid valuation methods to come up with a real-world
    value for the company.  The site is updated hourly, and has possibly been used at one of their
    VC meetings. The site can be viewed at \url{http://whatsminecraftsvalue.com/}




%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

